\begin{thebibliography}{99}

\bibitem{social1}
	Wade E., Dye J., Mead R., \& Matar M.,
	\emph{Assessing the Quality and Quantity of Social Interaction in a Socially Assistive Robot{--}Guided Therapeutic Setting}
	in IEEE International Conference on Rehabilitation Robotics
	(Zurich, Switzerland),
	June 2011
\bibitem{comedy1}
	Knight H., Satkin S., Ramakrishna V., \& Divvala S.,
	\emph{A Saavy Robot Standup Comic{:} Online Learning through Audience Tracking}
	in International Conference on Tangible and Embedded Interaction
	(Funchal, Portugal),
	January 2011

\bibitem{social2}
	Feil-Seifer D., \& Matari\'{c} M.,
	\emph{Human-Robot Interaction}. 
	Invited contribution to Encyclopedia of Complexity and Systems Science,
	Meyers R. (eds.),
	Springer New York,
	pp. 4643\textendash4659
	(2009) 

\bibitem{darpa1}
	DARPA Robotics Challege Home.
	Retrieved from \url{http://theroboticschallenge.org/}

\bibitem{zmp_human1}
	Muecke K. J.,
	(2009).
	\emph{An Analytical Motion Filter for Humanoid Robots}
	(Doctoral dissertation).
	Retrieved from
	\url{http://scholar.lib.vt.edu/theses/available/etd-04072009-183346/unrestricted/01-Body.pdf}

\bibitem{naogait1}
	Graf C., Hartl A., R\"{o}fer T., \& Laue T., 
	\emph{A Robust Closed-Loop Gait for the Standard Platform League Humanoid},
	in Proceedings of the Fourth Workshop on Humanoid Soccer Robots 
	in conjunction with the 2009 IEEE-RAS International Conference on Humanoid Robots, 
	Zhou C., Pagello E., Menegatti E., Behnke S., \& Rofer T. (eds.), 
	(Paris, France)
	pp. 30 – 37
	(2009)

\bibitem{icub_recog1}
	Browatzki B., Tikhanoff V., Metta G., B\"{u}lthoff H., \& Wallraven C.,
	\emph{Active Object Recognition on a Humanoid Robot}
	in IEEE International Conference on Robotics and Automation
	(Saint Paul, MN),
	May 2012,
	pp. 2021\textendash2028

\bibitem{vslam1}
	Wang Y., Lin M., \& Ju R.,
	(2010). 
	\emph{Visual SLAM and Moving-object Detection for a Small-size Humanoid Robot}, 
	International Journal of Advanced Robotic Systems, 
	Kordic V., Lazinica A., \& Merdan M. (eds.), 
	ISBN: 1729-8806, 
	InTech, DOI: 10.5772/9700. 
	Available from: \url{http://www.intechopen.com/journals/international_journal_of_advanced_robotic_systems/visual-slam-and-moving-object-detection-for-a-small-size-humanoid-robot}

\bibitem{path1}
    Gutmann J., Fukuchi M., \& Fujita M.,
    \emph{Real-time path planning for humanoid robot navigation},
    in Proceedings of the International Joint Conference on Artificial Intelligence,
    (2005),
    pp. 1232\textendash1237

\bibitem{path2}
	Berenson D., Abbeel P., \& Goldberg K.,
	\emph{A Robot Path Planning Framework that Learns from Experenice}
	in Proceedings from IEEE International Conference on Robotics and Automation,
	(Saint Paul, MN),
	May 2012,
	pp. 3671\textendash3678

\bibitem{path3}
	Dudekm, G. \& Jenkin, M. (2010).
	Representing and Reasoning About Space.
	In \emph{Computational Principles of Mobile Robotics}
	(2nd ed., pp 167-210).
	Cambridge University Press.


\bibitem{icub_net1}
	Stramandinoli F., Cangelosi A., \& Marocco D.,
	\emph{Towards the grounding of abstract words: A Neural Network model for cognitive robots}
	in Proceedings of the International Joint Conference on Neural Networks,
	(San Jose, CA),
	July 2011,
	pp. 467\textendash474

\bibitem{pr2_1}
	Rusu R., Holzbach A., Diankovl R., Bradskil G., \& Beetz M.,
	\emph{Perception for Mobile Manipulation and Grasping using Active Stereo}
	in Proceedings of the IEEE-RAS International Conference on Humanoid Robots,
	(Paris, France),
	Dec. 2009,
	pp. 632\textendash638

\bibitem{sea1}
	Pratt G. \& Williamson M.,
	\emph{Series Elastic Actuators}
	in Proceedings of the International Conference on Robotic Systems,
	1995,
	pp. 399\textendash406

\bibitem{our_paper1}
	Brooks G., Krishnamurthy P., Khorrami F.,
	\emph{Humanoid Robot Navigation and Obstacle Avoidance in Unknown Environments}
	in Proceedings of the Asian Control Conference,
	(Istanbul, Turkey)
	June 2013

\bibitem{KK05b_jirs}
	P.~Krishnamurthy and F.~Khorrami, 
	``{GODZILA}: A low-resource algorithm for path planning in unknown environments,'' 
	\emph{Jour. of Intelligent and Robotic Systems}, 
	vol.~48, no.~3, pp.~357--373, March 2007.

\bibitem{aldebaran1}
	Home - Corporate - Aldebaran Robotics|Accueil.
	Retrieved from \url{http://www.aldebaran-robotics.com/en/}

\bibitem{naodoc_motion1}
   	Locomotion control. 
   	NAO Software 1.14.3 documentation. 
   	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/motion/control-walk.html#control-walk}

\bibitem{naodoc_motion2}
	Locomotion control API.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/motion/control-walk-api.html#control-walk-api}

\bibitem{naodoc_motion3}
	Joint control.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/motion/control-joint.html}

\bibitem{NAOqi_overview1}
	NAOqi Framework.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/dev/naoqi/index.html}

\bibitem{qiBuild_tutorial1}
	qiBuild documentation.
	qiBuild 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/qibuild/index.html}

\bibitem{sonar_issues1}
	Marshall W.,
	\emph{Basics of Robot Sonar}
	Retrieved from \url{http://www.wgmconsulting.com/Sonar.pdf}

\bibitem{memory1}
	ALMemory. 
   	NAO Software 1.14.3 documentation. 
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/core/almemory.html}

\bibitem{sonar_ref1}
	Sonars.
	NAO Software 1.14.3 documentation. 
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/family/robots/sonar_robot.html}

\bibitem{sonar_ref2}
	ALSonar - Getting Started.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/sensors/alsonar.html?highlight=sonar#getting-started}

\bibitem{sonar_ref3}
	ALSonar API.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{https://community.aldebaran-robotics.com/doc/1-12/naoqi/sensors/alsonar-api.html#ALSonarProxy::subscribe__ssCR.iCR.floatCR}

\bibitem{naodoc_stiff1}
	Stiffness control.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/motion/control-stiffness.html#control-stiffness}

\bibitem{naodoc_track1}
	NAOqi Trackers.
	NAO Software 1.14.3 documentation.
	Retrieved from \url{http://www.aldebaran-robotics.com/documentation/naoqi/trackers/index.html}
\end{thebibliography}
