%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Platform Description
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Platform}\label{ch:platform}

The platform used consisted of bringing together three major pieces.
The Aldebaran Nao H25 was used for the mobile platform, the Hokuyo URG-04LX
Lidar was the sensor used for obstacle detection, and a custom mounting system
was built to mount the Lidar to the Nao.

% For this thesis we used the Nao as the mobile platform. Aldebaran makes him.
% He's a cool little robot and he allows us to explore both things we wanted to 
% look at which were navigation and gaiting. He's mobile, small, ``cost-effective''
% and has a good API that we can use to do lower-level control of things when we want to, 
% and abstract ourselves from it when we don't want to.
% The small size means he's easy to work with.
The Nao H25 Humanoid is made by Aldebaran Robotics. It is a small humanoid platform
which that can navigate a variety of indoor spaces but is safe for humans to 
work with without specialized safety equipment. It has a flexible API which allows
operates at a range of abstractions. It allows for low-level command of individual
joint angles when experimenting with gaiting and control algorithms or high-level
command of navigation vectors when working with path planning.
This makes the Nao an attractive mobile base for the topics covered in this thesis.

% While the Nao is cool and all, the sonar sensors just don't cut it for what we want to do.
% Lucky, Nao comes with a USB port and uses x86 and linux so it's relatively
% straightforward to add new things to him. Therefore, we added a better distance sensor.
% Specifically we added the Hokuyo URG-04LX-UG01.
% It's a good Lidar because it has a respectable range, good angular resolution,
% ``cost-effective'', and is kinda lightweight. Using this sensor we could do mapping 
% if we wanted to which means this system is extensible to the broader challenges 
% of the overall navigation problem such as SLAM\@. Using the Lidar we'll be able to 
% get enough information to do the job we need to.
To augment the Nao's sensor suite, the Hokuyo URG-04LX Lidar was added to the platform.
The URG allows for high resolution planar sensing of obstacles in the environment.
This is very important for effective navigation in unstructured environments.
The URG is also compact in size and light in weight making it appropriate
for mobile robotics applications.

% While it's easy to plug a USB cable into Nao's head, you still have to stick the Lidar somewhere.
% Nao doesn't have mount points that make it easy to add new hardware.
% Given that we have a nifty 3D printer (and I know Solidworks) we designed up a little suit of
% armor for Nao with a big stick coming out of it that we could mount the Lidar to, above his head.
% This works but the new dynamics destabilize Nao's default gait at certain speeds. 
% This doesn't mess with the navigation algorithm, but to increase the speed this will have to be dealt with,
% either by changing the rig or \ldots using the arms to counterbalance the new inertial forces as
% part of the walking gait.
To mount the Lidar to the Nao, a custom mount had to be designed and constructed.
The mount locates the Lidar around the torso of the Nao, which places it such
that it does not interfere with the locomotion of the robot while navigating
and minimizes the amount of motion seen by the Lidar due to gait oscillations.

Together, these three components comprised the platform used to perform experiments
in this thesis. The Chapter~\ref{ch:navigation} utilized all three of the major
components while in Chapter~\ref{ch:crawl_gait} only the Nao was used as the
Lidar would have interfered with the crawl gait.

\section{Hardware Overview}
% Ok so, three pieces of hardware here, the Nao, the Lidar, and the mount.
% Technically, all you need is the Nao since it is a mobile base with distance sensors but the sonars
% don't do that great so we added the Lidar, and since there's no where to screw it down we designed a mount.

The hardware assembled for this platform can be divided into three major parts,
the Nao H25 Humanoid Platform, a Hokuyo URG-04LX-UG01 Lidar, and a custom 3D
printed assembly to mount the Lidar to the Nao.
The Nao acted as the mobile base and provided onboard sensing and computation. 
Its large number of degrees of freedom and humanoid configuration were amenable
to the exploration of crawling algorithms.
The Nao is also equipped with two color cameras for viewing the environment
and two sonars for measuring the range to objects.
% TODO: Maybe this should be restructured to highlight the roles the platform
% played in the Crawling and Navigation experiments, referenced by chapter.
In the navigation experiment, the forward facing camera was used to estimate
the pose to a goal object.
Though the two sonars can be used for obstacle
avoidance, previous experimentation showed they
were insufficient for navigation. This is because in a number of scenarios the
specular refections would cause confusing readings and the low angular
resolution would prevent the robot from walking through traversable apertures.
To supplement the Nao's sensor suite, the URG Lidar was mounted to the robot
to provide accurate, high resolution range data for use with navigation.
As the Nao does not have any external mounting points, a custom mount was
designed and constructed to allow the URG to be mounted to the Nao.


% Subsections about each hardware piece.
\input{./chapters/platform/goal}
\FloatBarrier
\input{./chapters/platform/nao}
\FloatBarrier
\input{./chapters/platform/lidar}
\FloatBarrier
\input{./chapters/platform/mount}

% Need some sort of System or summary Section.
